### 2022-02-04 README.Rmd
readme

The initial codings pre-cleaning and reconciling intercoder agreement are also available. 
  - [icb_coder_crisis_sentence_event_aligned.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds)

@@

 - 01_compile_saves_and_align
    + compiles the original coding files into `./replication_data/temp/icb_coder_crisis_sentence_event.Rds`
    + the original coding files are not on the public repository; this can only be run by authors
    + aligns codings from multiple GUI versions on similar source sentences
    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
 - 02_format_and_clean
    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
 - 03_aggregation
    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.

@@

  - CaseStudy196
  - CaseStudy426
  - ICBEdataset_figure_metro_maps
  - ICBEdataset_figure_semantic_embeddings
  - ICBEdataset_paper_appendixICBCrises
  - ICBEdataset_paper_appendixVerbMeanings
  - ICBEdataset_paper_figure_prep
  - ICBEdataset_paper_PlotInterCoderAgreement

>>>>

@@

 - 01_compile_saves_and_align
    + compiles the original coding files into `./replication_data/in/icb_coder_crisis_sentence_event.Rds`. The original coding files are not on the public repository. Public users will load `icb_coder_crisis_sentence_event.Rds` directly.
    + aligns codings from multiple GUI versions on similar source sentences
    + creates `./replication_data/temp/ICBe_V1_long_unclean.Rds.Rds` (not included in online repo)
 - 02_format_and_clean
    + applies cleaning dictionaries to create `./replication_data/temp/ICBe_V1_long_clean.Rds` and `./replication_data/temp/ICBe_V1_long_clean.Rds` (not included in online repo)
 - 03_aggregation
    + applies aggregation algorithm to create `./replication_data/out/ICBe_V1_long_agreement.Rds`, `./replication_data/out/ICBe_V1_long_agreed.Rds`, `./replication_data/out/ICBe_V1_wide_agreed.Rds`.

@@

  - CaseStudy196
      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
  - CaseStudy426
  - ICBEdataset_figure_metro_maps
  - ICBEdataset_figure_semantic_embeddings
  - ICBEdataset_paper_appendixICBCrises
  - ICBEdataset_paper_appendixVerbMeanings
  - ICBEdataset_paper_figure_prep
  - ICBEdataset_paper_litreviewtable
  - ICBEdataset_paper_PlotInterCoderAgreement
